Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-07 acl.2016/acl2016.tex
acl paper

@@

We take a different approach by integrating the lexicalized model file into the translation model, reducing the need to query another model file. This resulted in a large decrease in decoding time, Figure~\ref{fig:lex-ro}.

\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{lex-ro.png}} 
\end{tabular}
\caption{Decoding time (in sec) with Compact Lexicalized Reordering, and integrated into a model the phrase-table}
\label{fig:lex-ro}
\end{figure}

>>>>

Figure~\ref{fig:mempool} compares the decoding time for Moses and our decoder, using the same models, parameters and test set. Our decoder is over 3 times faster with one thread, and 4.7\% faster using all cores. Like Moses, performance actually worsens after approximately 15 cores, however, the problem is not as pronounced. This gives us a better foundation on which to build further innovations for fast, multi-core decoding.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{mempool.png}} 
\end{tabular}
\caption{Decoding time of Moses and our decoder, using the same models}
\label{fig:mempool}
\end{figure}

@@

We take a different approach by integrating the lexicalized model file into the translation model, reducing the need to query another model file. This resulted in a large decrease in decoding time, especially with high number of cores, Figure~\ref{fig:lex-ro}. 
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{lex-ro.png}} 
\end{tabular}
\caption{Decoding time (in sec) with Compact Lexicalized Reordering, and integrated into a model the phrase-table}
\label{fig:lex-ro}
\end{figure} 
Integrating the lexicalized reordering model into the translation model decreases decoding time by 29\% with a single core but it is over 5 times faster using all cores. In fact, the decoding time with the integrated model is similar to that \emph{without} a lexilized reordering model. Critically for systems with large number of cores, it enables the decoder to continue to scale, making efficient use of all available cores, while using a separate lexicalized reordering model decoding time flatten out and actually worsens after approximately 10 threads.
